Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-03 presentation-plan/Plan_presentation_monday.tex
This is a MDP

>>>>

\noindent A Markov Decision Process has the form $M = (S, A, app, Pr, R)$

\begin{itemize}
	\item $S$ and $A$ are the finite set of states and actions
	\item $app(s)$ is the set of of actions applicable in $s$
	\item For every $a \in app(s)$, $Pr(s,a,s')$ is the probability of a state
		transition from $s$ to $s'$
	\item $R(s,a,s')$ is the \emph{reward} of the transition $(s,a,s')$.
\end{itemize}
